Supporting Information: The Transport Mechanisms of Polar Solutes in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2019-03-15 Ben_Manuscripts/transport/Supporting_Information.tex
Updates

\documentclass{article}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath} % or simply amstext
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\newcommand{\angstrom}{\textup{\AA}}
\newcommand{\colormap}{jet}  % colorbar to use
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
% Generated with solute_partitioning.py -t full_shifted.xtc -g berendsen.gro -r SOL -pr 1.6 --savename water_partitioning.pl
% in directory /home/bcoscia/Documents/Gromacs/equilibration/solvation_equilibration/NaGA3C11/offset/5wt
  \includegraphics[width=\textwidth]{5wt_offset_equil.pdf}
  \caption{5 wt \%}\label{fig:5wt_offset_equil}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{10wt_offset_equil.pdf}
  \caption{10 wt \%}\label{fig:10wt_offset_equil}
% Generated with solute_partitioning.py -t shifted.xtc -g last.gro -r SOL -pr 1.48 --savename water_partitioning.pl
% in directory /home/bcoscia/Documents/Gromacs/equilibration/solvation_equilibration/NaGA3C11/offset/10wt
  \end{subfigure}
  \caption{We created solvated systems with one third of the total water
	  initially placed in the tail region. (a) With 5 wt \% total water, the water
	  content equilibrates after 600 ns, with $\sim$ 72 \% of the total water in the
	  pores. (b) With 10 wt \% total water, the water content equilibrates after 100
	  ns, with $\sim$ 69 \% of the total water in the
	  pores.}\label{fig:solvation_equilibration}
  \end{figure}

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
% Generated with solute_partitioning.py -t PR.trr -g PR.gro -r SOL --savename SOL_partitioning.pl
% In directory /home/bcoscia/Documents/Gromacs/equilibration/xlink_equilibration/NaGA3C11/5wt
  \includegraphics[width=\textwidth]{5wt_offset_xlinked_equil.pdf}
  \caption{5 wt\%}\label{fig:5wt_offset_xlinked_equil}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{10wt_offset_xlinked_equil.pdf}
  \caption{10 wt\%}\label{fig:10wt_offset_xlinked_equil}
% Generated with solute_partitioning.py -t xlinked_equil.trr -g xlinked_equil.gro -r SOL -pr 1.48 --savename water_partitioning.pl
% In directory /home/bcoscia/Documents/Gromacs/equilibration/xlink_equilibration/NaGA3C11/10wt/63_percent
  \end{subfigure}
  \caption{The water content in the tail and pore region is not affected
  by cross-linking}\label{fig:solvation_equilibration}
  \end{figure}

@@

  We chose to model 6 solutes in each pore because there was a low degree of 
  interaction between solutes which gave us a sufficient number of independent 
  trajectories to observe and analyze. There are a negligible number of occurences
  % BJC: not sure what the appropriate cut-off should be
  where the center of a given solute came within 3.5 \AA of another same-solute
  center of mass.

  \begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{solute_interaction.pdf}
  \caption{Interactions between same-solutes are negligible when systems are 
  built with 6 solutes per pore. Even methanol, which interacts with other same-solute
  molcules the most, does so less than 0.05 \% of the time.}\label{fig:solute_interation}
  \end{figure}

>>>>

\documentclass{article}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath} % or simply amstext
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\newcommand{\angstrom}{\textup{\AA}}
\newcommand{\colormap}{jet}  % colorbar to use
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
\usepackage{xr}

\externaldocument[M-]{Outline}

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
% Generated with solute_partitioning.py -t full_shifted.xtc -g berendsen.gro -r SOL -pr 1.6 --savename water_partitioning.pl
% in directory /home/bcoscia/Documents/Gromacs/equilibration/solvation_equilibration/NaGA3C11/offset/5wt
  \includegraphics[width=\textwidth]{5wt_offset_equil.pdf}
  \caption{5 wt \%}\label{fig:5wt_offset_equil}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{10wt_offset_equil.pdf}
  \caption{10 wt \%}\label{fig:10wt_offset_equil}
% Generated with solute_partitioning.py -t shifted.xtc -g last.gro -r SOL -pr 1.48 --savename water_partitioning.pl
% in directory /home/bcoscia/Documents/Gromacs/equilibration/solvation_equilibration/NaGA3C11/offset/10wt
  \end{subfigure}
  \caption{We created solvated systems with one third of the total water
	  initially placed in the tail region. (a) With 5 wt \% total water, the water
	  content equilibrates after 600 ns, with $\sim$ 72 \% of the total water in the
	  pores. (b) With 10 wt \% total water, the water content equilibrates after 100
	  ns, with $\sim$ 69 \% of the total water in the
	  pores.}\label{fig:solvation_equilibration}
  \end{figure}

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
% Generated with solute_partitioning.py -t PR.trr -g PR.gro -r SOL --savename SOL_partitioning.pl
% In directory /home/bcoscia/Documents/Gromacs/equilibration/xlink_equilibration/NaGA3C11/5wt
  \includegraphics[width=\textwidth]{5wt_offset_xlinked_equil.pdf}
  \caption{5 wt\%}\label{fig:5wt_offset_xlinked_equil}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{10wt_offset_xlinked_equil.pdf}
  \caption{10 wt\%}\label{fig:10wt_offset_xlinked_equil}
% Generated with solute_partitioning.py -t xlinked_equil.trr -g xlinked_equil.gro -r SOL -pr 1.48 --savename water_partitioning.pl
% In directory /home/bcoscia/Documents/Gromacs/equilibration/xlink_equilibration/NaGA3C11/10wt/63_percent
  \end{subfigure}
  \caption{The water content in the tail and pore region is not affected
  by cross-linking}\label{fig:solvation_equilibration}
  \end{figure}

@@

  We chose to model 6 solutes in each pore because there was a low degree of 
  interaction between solutes which gave us a sufficient number of independent 
  trajectories to observe and analyze. There are a negligible number of occurrences
  % BJC: not sure what the appropriate cut-off should be
  where the center of a given solute came within 3.5 \AA of another same-solute
  center of mass.

  \begin{figure}[!htb]
  \centering
  \includegraphics[width=0.45\textwidth]{solute_interaction.pdf}
  \caption{Interactions between same-solutes are negligible when systems are 
  built with 6 solutes per pore. Even methanol, which interacts with other same-solute
  molcules the most, does so less than 0.05 \% of the time.}\label{fig:solute_interation}
  \end{figure}

  \subsection{Hydrogen Bond Detection Sensitivity}\label{section:hbond_sensisitivity}

  In Section~\ref{M-method:hbonds} of the main text, we established geometric criteria for the 
  identification of hydrogen bond interactions. Namely, if the distance between the donor,
  D, and acceptor, A, atoms is less than 3.5 \AA~and the angle formed by D--H...A is less
  than 30\degree, then we consider the interaction to be a consequence of hydrogen bonding.

  We tested the sensitivity of this criteria to ensure that our conclusions
  were not a strong function of the chosen criteria. In Figure~\ref{fig:hbond_sensitivity} we
  plotted the results of the same calculation performed to create Figure~\ref{M-fig:multi_hbonds}
  of the main text. We varied the distance cut-off between 3.0 and 4.0 \AA, and varied the
  angle cut-off between 25 and 35 \degree.

  As the distance and angle cut-offs are increased, there is a slight increase in the total
  number of hydrogen bonds, which is primarily manifested by an increased number of multiple-hydrogen-bond
  interactions. Using our most lenient set of criteria (d = 4.0 \AA~and $\theta$ = 35 $\degree$), glycerol,
  tetrose and ribose all show instances where they simultaneously hydrogen bond with 4 head group atoms.
  In the strictest case (d = 3.0 \AA~and $\theta$ = 25 \degree), ribose is the only solute with a 
  detected instance of a quadruple hydrogen bond.

  We can draw the same conclusions from any of the plots in Figure~\ref{fig:hbond_sensitivity}. 
  \begin{enumerate}
    \item An increased number of hydroxyl groups results in an increased number of hydrogen bond
    interactions.
    \item The number of multiple-hydrogen-bond interactions increases.
    \item On average, propylene glcyol participates in more hydrogen bond interactions than 
    ethylene glycol.  %BJC: might need to label the total hydrogen bonds (put number centered on top of bars)
  \end{enumerate}

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{\textwidth}
  \centering
  \includegraphics[trim={0 0.5cm 0.5cm 0.5cm}, clip, width=0.5\textwidth]{hbond_sensitivity_legend.pdf}
  \end{subfigure}
  \begin{subfigure}{\textwidth}
  \includegraphics[width=\textwidth]{hbond_sensitivity.pdf}
  \end{subfigure}
  \caption{We tested the sensitivity of our hydrogen bond detection to the chosen 
  geometric criteria for hydrogen bonding. We varied the distance cut-off between 3.0 and
  4.0 \AA, and varied the angle cut-off between 25 and 35 \degree.}\label{fig:hbond_sensitivity}
  \end{figure}
